Double trouble: Terrestrial ectortherm populations have both reduced opportunity for selection and physiological plasticity

### 2023-01-12 ms.rmd
Just adding details on traits

#########################
## Phylogeny
#########################
 ## Tree data
    tree_data <-  data_long %>%
                  group_by(species_full)                                                 %>%
                  mutate(n = length(habitat))                                            %>%
                  dplyr::select(species_full,  habitat, n)                               %>% 
                  distinct(species_full, habitat, n)
    #rownames(tree_data) <- tree_data$species_full
    #tree_data <- tree_data[,2:3]

@@

#### Affliations:
$^1$ Division of Ecology and Evolution, Research School of Biology, The Australian National University, Canberra, ACT 2600, Australia
$^2$ School of Biological, Earth and Environmental Sciences, University of New South Wales, Sydney, NSW, Australia
$^3$ SOLES, University of Sydney, Sydney, NSW, Australia
$^4$ Department of Biology, Lancaster University, Liverpool, UK

@@

>>>>

    # Traits 
      traits_habitat <- data_long2 %>%
                      group_by(habitat, trait_category) %>%
                      summarise(spp_n = length(unique(species_full)), k = n())
      traits_all <- data_long2 %>%
                      group_by(trait_category) %>%
                      summarise(spp_n = length(unique(species_full)), k = n())
#########################
## Phylogeny
#########################
 ## Tree data
    tree_data <-  data_long %>%
                  group_by(species_full)                                                 %>%
                  mutate(n = length(habitat))                                            %>%
                  dplyr::select(species_full,  habitat, n)                               %>% 
                  distinct(species_full, habitat, n)
    #rownames(tree_data) <- tree_data$species_full
    #tree_data <- tree_data[,2:3]

@@

#### Affliations:
$^1$ Division of Ecology and Evolution, Research School of Biology, The Australian National University, Canberra, ACT 2600, Australia
$^2$ Ecology and Evolution Research Centre, School of Biological, Earth and Environmental Sciences, University of New South Wales, Sydney, NSW, Australia
$^3$ SOLES, University of Sydney, Sydney, NSW, Australia
$^4$ Department of Biology, Lancaster University, Liverpool, UK

@@

Most of the effect size estimates came from measurements of metabolic rates (both resting and maximal -- $N_{species}$ = `r mr <- traits_all %>% filter(trait_category %in% c("rest_MR", "max_MR")); sum(mr[,"spp_n"])`, $N_{effects}$ = `r sum(mr[,"k"])`, considering acute and acclimation effects together), metabolic enzymes ($N_{species}$ = `r me <- traits_all %>% filter(trait_category %in% c("metabolic_enzyme", "ATPase")); me[,"spp_n"]`, $N_{effects}$ = `r me[,"k"]`) and whole-organism performance traits (i.e., sprint speed and endurance -- $N_{species}$ = `r per <- traits_all %>% filter(trait_category %in% c("sprint", "endurance")); sum(per[,"spp_n"])`, $N_{effects}$ = `r sum(per[,"k"])`).
